Visualizations for article

### 2016-05-25 101-visualizations-for-article.Rmd
Add a couple spectrographs
Fix widths/heights of spectrograms

@@

@@

```{r}
spectrogram("MD1855", best_matches, white_list = 7)
```

@@

@@

```{r}
spectrogram("NY1876", best_matches, white_list = 8)
```

```{r}
spectrogram("NY1879", best_matches, white_list = 8)
```

>>>>

```{r setup,}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

CA1851

```{r}
spectrogram("CA1851", best_matches, white_list = 3)
```

@@

```{r, fig.height=3}
spectrogram("MD1855", best_matches, white_list = 7)
```

@@

NV1861

```{r}
spectrogram("NV1861", best_matches, white_list = 4)
```

@@

```{r, fig.height=6.5}
spectrogram("NY1876", best_matches, white_list = 8)
```

```{r, fig.height=7.75}
spectrogram("NY1879", best_matches, white_list = 3)
```
